\documentclass{article}
\usepackage[margin=1 in]{geometry}
\usepackage{parcolumns}
\newcommand{\personA}[1]{\colchunk{\begin{description}\item[A:~~]{#1}%
    \end{description}}}
\newcommand{\personB}[1]{\colchunk{\begin{description}\item[B:~~]{#1}%
    \end{description}}\colplacechunks}

\begin{document}

\centerline{\LARGE A Fork-Based Pull Request}

\qquad

\begin{parcolumns}[colwidths={1=3.2 in, 2=3.2 in},nofirstindent]{2}
%
  \personA{\emph{If not done already:}
    \\ Create an empty repository on GitHub.
    \\ Name it \texttt{sample\_[your name]}.
    \\ Connect your \texttt{sample} repo to it:
    \\ \texttt{git remote add origin [your\_repo\_url]}
    \\ Put your work on GitHub:
    \\ \texttt{git push origin master}}
  \personB{Relax.}
%
  \personA{Relax.}
  \personB{Clone their repository on GitHub:
    \\ \texttt{git clone [their\_repo\_url]}
    \\ Navigate to their GitHub repo page, and fork their repo
       by clicking ``Fork.''
    \\ Connect your local clone to your fork:
    \\ \texttt{git remote add my\_fork [your\_fork\_url]}}
%
  \personA{Working on master
   \\ (\texttt{git checkout master}):
   \\ Add a comment to the code in \texttt{R/square.R} that does the calculation.
   \\ Commit the work:
   \\ \texttt{git commit -a -m '\ldots'}
   \\ Push the work to GitHub:
   \\ \texttt{git push origin master}}
  \personB{Working on a separate branch
   \\ (\texttt{git checkout -b my\_branch}):
   \\ Add your name to the copyright notice in
   \\ \texttt{README.md}.
   \\ Commit the work:
   \\ \texttt{git commit -a -m '\ldots'}
   \\ Push the work to GitHub:
   \\ \texttt{git push my\_fork my\_branch}}
%
  \personA{Relax.}
  \personB{Grab their work:
   \\ \texttt{git checkout master}
   \\ \texttt{git pull origin master}
   \\ Add their work to your fork:
   \\ \texttt{git push my\_fork master}
   \\ Merge their work into your branch:
   \\ \texttt{git checkout my\_branch}
   \\ \texttt{git merge master}
   \\ Add your merge to your fork:
   \\ \texttt{git push my\_fork my\_branch}
   \\ Go to the GitHub page for your fork. Find your branch \texttt{my\_branch}.
      Click on ``New Pull Request.''
   \\ Send them a message on the pull request page---you can tag them with
      \texttt{@[username]} and explain the work you've done.
      ``Assign'' them to review the pull request.}
%
  \personA{Go to your GitHub page.
    Find their pull request.
    Read their commentary and look at their code changes.
    Click on the line where they changed the copyright.
    Complain about it some\-how---maybe that something should or should not be
    abbreviated.}
  \personB{Relax.}
%
  \personA{Relax.}
  \personB{Go to your pull request.
   Read their commentary.
   \\ Go to your branch:
   \\ \texttt{git checkout my\_branch}
   \\ Fix the copyright in \texttt{README.md} to comply with their request.
   \\ Commit your work:
   \\ \texttt{git commit -a -m '\ldots'}
   \\ Push the work to your fork:
   \\ \texttt{git push my\_fork my\_branch}}
%
  \personA{Now you're happy. Click ``Merge Pull Request'' and confirm.
    Click ``Delete Branch.''}
  \personB{Relax.}
%
  \personA{Update your local version of the codebase:
   \\ \texttt{git pull origin master}}
  \personB{Get the successfully merged version:
   \\ \texttt{git checkout master}
   \\ \texttt{git pull origin master}
   \\ Update your fork:
   \\ \texttt{git push my\_fork master}
   \\ Delete your local branch:
   \\ \texttt{git branch -d my\_branch}
   \\ Delete your branch on your fork:
   \\ \texttt{git push my\_fork :my\_branch}}
%
\end{parcolumns}
\end{document}
